### 2013-06-26 Tex/chapters/results.tex
Korrekturen, Umfärbung
Kurze Beschreibung der g* Werte

@@

        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}

@@

    Where \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} is
    the Binder cumulant and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)

@@

    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}

@@

\subsection{Critical Temperature}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\), which are plotted in
    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted which is evidently correlated with \(T_c\).
    That is plausible, because \(T_c\) is dependend on the coupling
    constant \(J\) (compare \eqref{eq:exactTc}).\\
    It seems reasonable to normalize the values of \(T_{c}\) by
    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }

@@

    %~ <J>\(\sigma\), Anmerkung zur Anomalie des GG und der Ähnlichkeit von <J> zu \(T_c\)\\
%~
    %~ Erklärung zu Autokorreltationszeit \(\tau\) und Equilibrierungszeit \(t_eq\)\\
    %~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
    %~ Bestimmung der kritischen Punkte\\
        %~ Polyfit 4ten Grades durch Binder Kumulante \cite{Binder1981}\\
        %~ Finite Size Scaling Vergleich der Exponenten (AutoScale \cite{Melchert2009}, Vergleich \cite[S. 59]{Pelissetto2002})\\

>>>>

    % Ausfuehrlichere Herleitung der Skalentheorie, Skalenanalyse

@@

        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
        \label{eq:binderCumulant}
        g &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}

@@

    Where \(g\) from eq. \eqref{eq:binderCumulant} is a normalized
    Binder cumulant \cite{Binder1981} and \(\tilde{M}, \tilde{C}\) and \(\tilde{G}\)

@@

    To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}

@@

\subsection{Critical Temperature}
\label{ssec:binderIntersections}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\), which are plotted in
    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted which is evidently correlated with \(T_c\).
    That is plausible, because \(T_c\) is dependend on the coupling
    constant \(J\) (compare \eqref{eq:exactTc}).\\
    It seems reasonable to normalize the values of \(T_{c}\) by
    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }

@@

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g^*\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses an other definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match it's definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g^*\) anyway, it is easy to check the consistency and
    behaivior of \(g^*\) in the disordered Ising modell.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a Relative Neighborhood graph][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a Gabriel graph][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder cumulant at the critical point $g^*$]
        {
            Values of the Binder cumulant at the critical point \(g^*\)
            for\\
            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in fig. \ref{fig:TcG}, \(g^*\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviation is less than \(1\%\). Perhaps this is some inherent flaw
    of the cubic spline interpolation used to aquire these \(g^*\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g^*\) much, as expected.

%~ Darstellung von Suszeptibilität \(\chi\), spezifischer Wärme \(c\), mittlerer Magnetisierung \(<m>\) über Unordnungsparamter \(\sigma\)\\
